---
title: "Lab 01 - Hello R"
author: "Saima Arina"
date: "01/20/2026"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

There are 1846 rows and 3 columns. The variables included are: dataset, x-values, and y-values. 

```{r}
data("datasaurus_dozen")

datasaurus_dozen %>%
  count(dataset) %>%
  print()
#> # A tibble: 13 × 2
#>    dataset        n
#>    <chr>      <int>
#>  1 away         142
#>  2 bullseye     142
#>  3 circle       142
#>  4 dino         142
#>  5 dots         142
#>  6 h_lines      142
#>  7 high_lines   142
#>  8 slant_down   142
#>  9 slant_up     142
#> 10 star         142
#> 11 v_lines      142
#> 12 wide_lines   142
#> 13 x_shape      142
```


### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The data is visualized in a plot to show a non-linear relationship between the x and y variable, illustrated as a dinosaur. The resulting correlation coefficient is -0.06, but not relevant due to the non-linear nature.


### Exercise 3

This is your turn to write the code and narrative for the star dataset. Follow the same steps as above to complete the analysis. Don't forget to label your chunks appropriately!

Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.

```{r plot-star}

```

I'm some filler text, you should replace me with more meaningful text...

```{r cor-star}

```
Add your explanation here—what did you notice?


### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r}

```

```{r}

```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


